\documentclass[10pt,a4paper,]{article}
\usepackage{fontspec}
\usepackage{microtype}
\begin{document}
\section*{lilypond.org Website structure}

Analysis and improvement considerations by Urs Liska.

\subsection*{Front Page}
Very short, very concise, good.\\
Starting text may be extended a little bit (but I won't touch it in the first improvement step).\\
Points to:

\subsection*{Introduction}
	\begin{itemize}
	\item \textbf{Our Goal}\\
		Idea is good but second paragraph is somewhat illogical.\\
		Could be slightly more elaborate.\\
		Maybe rename to \textbf{“Our Mission”}?
	\item\textbf{What LilyPond does}\\
		Simply links\\
		--- Features: Good\\
		--- Examples: Good\\
		--- Freedom: What does it do here?\\
		--- Background: What does it do here?
	\item \textbf{LilyPond in use}\\
		Simply links\\
		--- Productions\\
		--- Reviews\\
		Good. But maybe something from Community should be linked here too?
	\item \textbf{How LilyPond works}\\
		Simply links\\
		--- Text input: Good\\
		--- Easier Editing: Good, but rename to “Editing”
	\end{itemize}
	Has to be considerably restructured.\\
	Maybe make sections:\\
	\begin{itemize}
	\item \textbf{Our Mission}
	\item \textbf{What Sets LilyPond Apart:}\\
	--- Features\\
	--- Examples\\
	--- Text Input\\
	--- Editing (not “Easier”)\\
	--- Background\\
	--- Freedom\\
	I think the page order below \emph{Introduction} should be changed to this order.\\
	\emph{Productions} and \emph{Reviews} should be moved to \emph{Community}.
	\item \textbf{Read more about LilyPond:}\\
	--- Reviews\\
	--- Productions\\
	--- Publications (what we wrote)\\
	--- Scores of Beauty\\
	--- Mailing Lists and Support\\
	--- Getting involved ($\rightarrow$ "Help us" page)\\
	\end{itemize}
	As a first step simply link to the existing pages. But these pages will have to be restructured too.\\
	Probably the order in the "Read more" section should more or less become the structure of \emph{Community} (or at least directly reflect this).

\paragraph{Suggested First Improvement}
In a first step I would
\begin{itemize}
\item Rearrange the link lists and pages as outlined above
\item Slightly modify the \emph{Our Goal} box
\item Rewrite \emph{Editing}, mainly by adding an introduction to that page.
\end{itemize}

\vfill
\pagebreak
\subsection*{Introduction$\rightarrow$Features}
This page is \emph{very} problematic! Has to be completely restructured\\
A big problem here is that much of the information is redundant.

The following section is just the analysis, later I'll make a suggestion for restructuring the page.

\subsubsection*{Elegance}
\begin{itemize}
\item \textbf{Excellent classical engraving}\\
This is OK. Maybe one has to be slightly more elaborate to make clear why this is something different than \emph{Our Goal (Our Mission)} (but this can be postponed).
\item \textbf{Effective Layout Choices}\\
This should rather move to \emph{Usability (Ease of use)}
\end{itemize}

\subsubsection*{Ease of use}
I would completely drop the Term \emph{Ease of use}.
This is a buzz phrase that simply doesn't match reality.
In any case it's not the feature that sets LilyPond apart.
This will fall on our toes because a new user won't experience LilyPond like this.\\

\begin{itemize}
\item \textbf{Text based input}\\
This has to be enhanced.
It is clearly written by people who are familiar with the concept.\\
The sentence about "no need to remember complex command sequences" is nonsense: This might appeal to an Emacs user, but not to a Finale user ;-).
Instead extend on what text based input really offers.
Is it OK to link to my lilypondblog.org post here?
\item \textbf{Mix music and text}\\
Basically good.
Maybe add a reference to the MediaWiki extension?
\item \textbf{Accessibility}\\
Good.
Maybe add a link to the score on the \emph{Examples} page?
\item \textbf{Extensible design}\\
This is basically good, but should be made clearer and somewhat more elaborate.\\
But surely not under \emph{Ease of use}.
This is clearly a toplevel \emph{Feature}.
\end{itemize}

\subsubsection*{Environment}
This term has to be reconsidered.
It's basically OK but somewhat meaningless.

\begin{itemize}
\item \textbf{Free Software}\\
Make much shorter and simply link to the dedicated page.
\item \textbf{Excellent Support}\\
Good, but could be made more elaborate.\\
“the development team makes sure that problems are solved quickly” isn't really true.
Could turned into a better selling point, sth like: “Often you get a solution within hours, and it happens regularly that such solutions will be soon integrated in the product”.
\item \textbf{Enhanced Editors}\\
Make slightly shorter and simply link to \emph{Editing} page.
\end{itemize}

\subsubsection*{Missing items:}
\begin{itemize}
\item Version control
\item Robustness of tweaks
\end{itemize}



\section*{Miscellaneous wishes}
\begin{itemize}
\item Move \emph{Essay} to \emph{Introduction} and\\
remove the \emph{Background} placeholder.\\
-> Impossible because \emph{Essay} isn't a web page but a manual.
\item Move \emph{Productions} and \emph{Reviews} to \emph{Community}
\item Add an item \emph{Tools using LilyPond} to the \emph{Productions} page.\\
For example the MediaWiki extension, AnkiLilyPond, lilybin, schikkers-list.
\end{itemize}
\end{document}